---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# yose (寄席)

This package implements incremental figure display in {revealjs} slide.
`yose` is a Japanese word meaning storytelling [-> Google Images](https://www.google.co.jp/search?q=%E5%AF%84%E5%B8%AD&source=lnms&tbm=isch&sa=X&ved=0ahUKEwix35LSoYHaAhVJlJQKHQKKARYQ_AUICygC&biw=1280&bih=924).


## Usage

You can install the latest development version from github with

```{r, eval = F}
# install.packages("devtools") # if not installed
devtools::install_github("KeachMurakami/yose")
```

Try the following minimal `.rmd`.

```{r}
#> ---
#> output: revealjs::revealjs_presentation
#> ---
#> 
#> ```{r setup}
#> library(knitr)
#> library(tidyverse)
#> library(yose)
#> yose::set_reveal_hooks()
#> 
#> p <-
#>  lapply(2:5, function(x){
#>    tibble(x = 1:5, y = x * 2)[1:x, ] %>%
#>      ggplot(aes(x, y)) +
#>      geom_point() +
#>      geom_line() +
#>      lims(x = c(0, 5), y = c(0, 10))
#>  })
#> ```
#> 
#> # Section1
#> 
#> ## Section1-1
#> 
#> <div style="position:relative; top:0px; width:800px; height:600px; margin:0 auto;">
#> ```{r fragment_index = 1, echo = F}
#> plot(mtcars$mpg, mtcars$disp)
#> ```
#> 
#> ```{r fragment_style = 'fragment fade-up', fragment_index = 3, echo = F}
#> plot(mtcars$mpg, mtcars$disp)
#> text("a", x = 30, y = 400)
#> ```
#> </div>
#> <div class="fragment" data-fragment-index="2">- plot points</div>
#> <div class="fragment" data-fragment-index="4">- add a comment</div>
#> 
#> ## Section1-2
#> 
#> demo: `kamishibai`
#> 
#> `r yose::kamishibai(p)`
#> 
```

## LICENCE

This package is free and open source software, licensed under GPL.

## Session information

```{r sessioninfo, echo = F}
library(knitr)
library(revealjs)
library(rmarkdown)
devtools::session_info()
```
